\textls[-0]{\thetitle}

### 2023-03-03 metatheory-condensed.tex
wording

\item
\TT also features \emph{linkage transformers}, used to model the features like inheritance, extending and overriding components in \Lang .
\item
Inductive types are modeled as W-types~\cite{martin1984intuitionistic} and their
extension as overriding.

>>>>

\item
\TT features \emph{linkage transformers}, which model how a family can be
inductively constructed by inheriting fields from another family,
adding new fields, or overriding existing fields.
\item
Inductive types are modeled as W-types~\cite{martin1984intuitionistic} and their
extension as overriding.
